---
title: "Minicore experiments"
output:
  html_document:
    df_print: paged
---

```{r libs, message=FALSE}
library(ggplot2)
library(dplyr)
library(tidyr)
library(knitr)
library(cowplot)
library(grid)
library(gridExtra)
```

```{r wd}
setwd('~/git/minicore-experiments')
```

```{r kmpp_parse}
m <- read.table('kmeanspp_exp/kmpp_merged.csv', header=T, sep=',')
m$value <- ifelse(m$value > 1e300, NA, m$value)
```

```{r grid_arrange_shared_legend}
grid_arrange_shared_legend <- function(..., ncol = length(list(...)), nrow = 1, position = c("bottom", "right")) {

  plots <- list(...)
  position <- match.arg(position)
  g <- ggplotGrob(plots[[1]] + theme(legend.position = position))$grobs
  legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
  lheight <- sum(legend$height)
  lwidth <- sum(legend$width)
  gl <- lapply(plots, function(x) x + theme(legend.position="none"))
  gl <- c(gl, ncol = ncol, nrow = nrow)

  combined <- switch(position,
                     "bottom" = arrangeGrob(do.call(arrangeGrob, gl),
                                            legend,
                                            ncol = 1,
                                            heights = unit.c(unit(1, "npc") - lheight, lheight)),
                     "right" = arrangeGrob(do.call(arrangeGrob, gl),
                                           legend,
                                           ncol = 2,
                                           widths = unit.c(unit(1, "npc") - lwidth, lwidth)))
  grid.newpage()
  grid.draw(combined)
  # return gtable invisibly
  invisible(combined)
}
```

### First result

* MC and MCLS both faster than SKL
    * Though note that as of 3/8/2021, the results are not really comparable as SKL only uses 1 thread
* MC and MCLS competitive with, usually lower objective than SKL, with MCLS usually the lowest

```{r kmpp_time_1t_time}
#kable(m %>% filter(nthreads == 1 & measure == 'time') %>% select(-orig_name, -measure) %>% transform(value = as.character(signif(value, digits=3))))
```

```{r kmpp_time_1t_cost}
#kable(m %>% filter(nthreads == 1 & measure == 'cost') %>% select(-orig_name, -measure) %>% transform(value = as.character(signif(value, digits=5))))
```

```{r kmpp_plot}
kmpp_plot <- function(m, distance='SQRL2',
                      nthreads=4, measure='time',
                      kmin=25,
                      sparsity='sparse', logy=F)
{
  measure_pretty <- if(measure == 'time') {
    if(logy) {'Log10(time in seconds)'} else {'Time in seconds'}
  } else {
    'K-means objective cost'
  }
  m$name <- plyr::mapvalues(m$name, from=c('MC_KMLSpp', 'MC_KMpp', 'SKL'),
                            to=c('Minicore KM++LS++', 'Minicore KM++', 'Scikit-learn KM++'))
  mfilt <- m %>% filter(distance == !!distance & nthreads == !!nthreads &
                        measure == !!measure & k >= kmin &
                        sparsity == !!sparsity)
  title_suffix <- paste0('(', sparsity, ')')
  pl1 <- mfilt %>% filter(dataset == 'PBMC') %>%
    ggplot(aes(x=k, y=value, color=name)) +
      geom_line() + geom_point() + theme_bw() +
      theme(legend.title = element_blank()) +
      labs(y=measure_pretty, title=paste('PBMC', title_suffix))
  pl2 <- mfilt %>% filter(dataset == 'Cao2m') %>%
    ggplot(aes(x=k, y=value, color=name)) +
      geom_line() + geom_point() + theme_bw() +
      theme(legend.title = element_blank()) +
      labs(y=measure_pretty, title=paste('Cao2m', title_suffix))
  pl3 <- mfilt %>% filter(dataset == 'Cao4m') %>%
    ggplot(aes(x=k, y=value, color=name)) +
      geom_line() + geom_point() + theme_bw() +
      theme(legend.title = element_blank()) +
      labs(y=measure_pretty, title=paste('Cao4m', title_suffix))
  if(logy) {
    pl1 <- pl1 + scale_y_continuous(trans='log10')
    pl2 <- pl2 + scale_y_continuous(trans='log10')
    pl3 <- pl3 + scale_y_continuous(trans='log10')
  }
  grid_arrange_shared_legend(pl1, pl2, pl3)
}
```


```{r kmpp_time_sparse}
kmpp_plot(m, nthreads=1, kmin=2, sparsity='sparse', measure='time', distance='SQRL2', logy=F)
```

```{r kmpp_time_dense}
kmpp_plot(m, nthreads=1, kmin=2, sparsity='dense', measure='time', distance='SQRL2', logy=T)
```
```{r kmpp_cost_sparse}
kmpp_plot(m, nthreads=1, kmin=2, sparsity='sparse', measure='cost', distance='SQRL2', logy=F)
```
```{r kmpp_cost_dense}
kmpp_plot(m, nthreads=1, kmin=2, sparsity='dense', measure='cost', distance='SQRL2', logy=F)
```

### Second result

* Even the slowest distance is not _much_ slower than the fastest

```{r kmpp_dist_t16}
m %>% filter(nthreads == 16 & measure == 'time' & name == 'MC_KMpp' & sparsity == 'sparse' & dataset %in% c('Cao2m', 'Cao4m')) %>%
  ggplot(aes(x=as.numeric(k), y=as.numeric(value), color=distance)) +
    geom_point() + facet_grid(~dataset, scales="free_y") + theme_bw() +
    labs(x='k', y='Time in seconds') + theme(legend.title = element_blank())
```

```{r kmpp_dist_t4}
m %>% filter(nthreads == 4 & measure == 'time' & name == 'MC_KMpp' & sparsity == 'sparse' & dataset %in% c('tiny', 'PBMC')) %>%
  ggplot(aes(x=as.numeric(k), y=as.numeric(value), color=distance)) + geom_point() + facet_grid(~dataset, scales="free_y")
```

### Third result

* MC and MCLS both yield better downstream k-means objectives compared to SKL
* Our minibatch k-means handles the various distances
